---
title: "MachineLearningExercise"
author: "pengweicmu"
date: "January 31, 2016"
output: html_document
---

A SVM model has been selected to as the final model to train the training data and cross validated with validation data. The SVM model then used on testing data set and produce a 100% accuracy output.

Several other models have been tested out and discarded due to low accuracy on validation data, as compared with SVM. An example of using Trees is included here just for reference.

```{r}
library(caret)
# SVM from package e1071  
library(e1071)

# Read data after pre-processing from pml-training-clean.csv
testingDataClean<-read.csv("pml-testing.csv")
trainingDataClean<-read.csv("pml-training-clean.csv")

# List of Factors selected as independent factors after preprocessing of data
summary(trainingDataClean)

# Partition training data into train and validation
inTrain<-createDataPartition(y=trainingDataClean$classe,p=0.8,list=FALSE)
trainData<-trainingDataClean[inTrain,]
testing<-trainingDataClean[-inTrain,]

# Tree is selected as the first round test
modelfitTree<-train(classe~.,method="rpart",data=trainData)
validationTree<-predict(modelfitTree,testing)
# Accuracy on validation data is extremly low
confusionMatrix(testing$classe,validationTree)

# SVM is selected as the second round test
modelfitSVM<-svm(classe~.,data=trainData)
validationSVM<-predict(modelfitSVM,testing)
# Accuracy on validation data is extremly high
confusionMatrix(testing$classe,validationSVM)

# SVM is selected as the final model on test data
prediction<-predict(modelfitSVM,testingDataClean)
prediction
```

The plot is generated using Trees, it is used to generate first intuitive understanding of data. It is not used for testing data since SVM model is selected as the final model:

```{r, echo=FALSE}
rattle::fancyRpartPlot(modelfitTree$finalModel)
```


